Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Remove trailing whitespace

Many Haskell programmers tend not to write test code even though the
strong type system of Haskell cannot always ensure correct semantics.
Test code helps users to understand the usage of
functions and developers to maintain semantics
while extending software. To ease the production and enhance the value of test code, we
propose to carry out behavior driven development with two tools:
Doctest integrated with QuickCheck for user documentation and Hspec
with combinators extended for code documentation. With our
method, specification can be used for documentation and automatic
testing. This kill-three-birds-with-one-stone aspect would motivate
Haskellers to write test code.

@@

@@

\begin{quote}
    \emph{kazu: I would like to add the following:}

So, we need common syntax to describe examples and properties
independently in Haddock. Doctest should automatically verify
examples and test properties.
\end{quote}

@@

\begin{quote}
    TBD: sol: @kazu, can you update this?
\end{quote}

@@

\begin{itemize}
\item
    The Haskell community does not have common syntax to describe
    evidence with Haddock markup syntax.
\item
    The Haskell community does not have a BDD tool for user documentation.
\item
    Hspec does not provide combinators to express expectations with
    BDD terminology.
\end{itemize}

@@

\begin{itemize}
\item Define new Haddock markup for examples.
\item Define new Haddock markup for properties.
\item Bring Doctest from the Python community to the Haskell
community and integrate it with QuickCheck.
\end{itemize}

@@

Evidence in comments is automatically
tested by the Doctest command. We also provided a library
to do this job. Its implementation will discussed in Section~\ref{sec:doctest}.

>>>>

When wading through the numerous libraries written by
the Haskell community, one sometimes gets the impression that the type
system is being too much relied on, at the expense of testing.
While the type system cannot always guarantee semantic correctness,
test code has more applications than getting the code correct.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
QuickCheck integrated in Doctest for user documentation and Hspec
with new mnemonic combinators for code documentation.
Our method utilizes specification that can also be used for
documentation and automatic testing. We hope that this three-in-one
quality motivates Haskellers to write more test code.

@@

\begin{quote}
    \emph{kazu: Monoid is already described in Introduction. Why is this repeated? And ``code documentation'' is aslo already dicussed in Introduction. I think we can use ``code documentation'' here.}
\end{quote}

@@

So, we need common syntax to describe examples and properties
independently in Haddock. Doctest should automatically verify
examples and test properties.

@@

@@

\begin{itemize}
\item
    For user documentation,
    Haddock does not have markups to describe evidence.
\item
    For code documentation,
    Hspec does not provide combinators to express expectations with
    BDD terminology.
\end{itemize}

@@

\begin{itemize}
\item Define new Haddock markup for examples.
\item Define new Haddock markup for properties.
\item Bring Doctest from the Python community to the Haskell
community and integrate it with QuickCheck.
Examples and properties in Haddock comments is automatically
tested by the Doctest command.
Its implementation will be discussed in Section~\ref{sec:doctest}.

@@
